Accelerated evolution of convective simulations

### 2018-06-12 tex/bvp_paper.tex
updates conclusion and appendix text

The Nusselt number (Nu) quantifies the efficiency of convective heat transport
and is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
When $S < 10^{3.67}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a time-stationary value of Nu, and is thus
in a state of constant convective heat transport.
At larger $S$ in 2D, the value of Nu varies significantly over time,
as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
AE runs in Fig.~\ref{fig:oscillating_plumes}. We find that these systems exhibit
large Nu during
states in which temperature fluctuations travel in their natural buoyant
direction (Fig.~\ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
with oppositely signed fluid, Nu is suppressed (Fig.~\ref{fig:oscillating_plumes}, Ib and IIb, 
where warm fluid is pulled down by the downflow
lane, and cool fluid is drawn up by the upflow lane). The plumes in these
systems naturally oscillate horizontally over time, switching between transport being dominated
by a counterclockwise cell, as pictured in Fig.~\ref{fig:oscillating_plumes}, and
a clockwise cell. Our choice of no-slip
boundary conditions prevents the fluid from entering a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable. However, thanks to our choice of periodic
boundary conditions and despite the no-slip conditions, the full system of the
upflow and downflow plumes is free to slowly migrate to the left or right over time,
and we observe this phenomenon in our solutions.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. 
This time-dependent behavior of Nu is not seen strongly in our 3D solutions,
however most 3D simulations we conducted were at low $S$ compared to the runs in
which this behavior was observed in 2D.

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
\caption{The time variation of the Nusselt number is shown for two AE cases at
$S = 10^5$ (top) and $S = 10^7$ (bottom). On the left, the instantaneous value of Nu
is shown as a function of time. On the right, temperature snapshots are shown for
Nu maxima (Ia \& IIa) and minima (Ib \& IIb). The suppressed value of Nu at the
minma arises from entrainment of fluid elements whose temperature perturbations
are wrongly signed (e.g., hot material going downwards and cold material going
upwards in Ib \& IIb). The colorbar scaling of panels Ia\&b are the same, as
are the scalings of panels IIa\&b. 
The minimum temperature is chosen by the fixed-temperature
boundary condition at the top, $T_{\text{top}} = -0.5$. The decreased range of
the colorbar scaling for
for IIa\&b was chosen to better display the convective dynamics.
\label{fig:oscillating_plumes} }
\end{figure}

\begin{figure}[b!]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement and denote 2D (purple circles) and 3D (red stars). 
The run at $S = 10^5$ marked as a
black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
Vertical lines represent the standard deviation of the measurement,
and quantify natural variation over the averaging window. 
(a) Nu scales as Ra$^{1/5}$; at high $S$ in 2D the value of Nu fluctuates over time
(see Fig.~\ref{fig:oscillating_plumes}).  
(b) Re, which measures turbulence in the solution, scales as
Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at the fixed-temperature
top boundary is shown; this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
Relative error for measurements of (d) Nu, (e) Re, and (f) $\angles{T} - T_{\text{top}}$ between 
AE solutions and SE solutions are shown.
The greyed area of the plots indicates the region in which only AE runs were
carried out due to computational expense. \label{fig:parameter_space_comparison} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
(d-f) The KS profiles, as defined in Eqn.~(\ref{eqn:ks_profile}),
are shown for the related distributions; solid lines indicate positive values
while dashed lines are negative values. Unlike the temperature distributions in
Fig.~\ref{fig:temp_comparison}, these distributions
show very good agreement and small values of the KS statistic.
\label{fig:pdf_comparison} }
\end{figure}

%%%%%%%%%%%%
%%%%%%%%%%%
% SPEEDINESS OF AE vs SE
%%%%%%%%%%%
%%%%%%%%%%%%

\section{Computational Benefits of AE}
\label{sec:speedups}

\begin{table}
\caption{
}
\label{table:speed}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X }
\hline																	
$S$	&	nz, nx, ny	&	$t_{\text{sim,AE}}/t_{\text{sim,SE}}$	&	
$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$		\\
\hline \hline \multicolumn{4}{c}{\vspace{-0.2cm}}\\
\multicolumn{4}{c}{\vspace{0.1cm}2D Runs} \\
\hline
$10^1$	&	32,	64	&	2.32    & \\
$10^2$	&	64,	128	&	0.905   & 2.03  & 4.369 &  2.152    \\
$10^3$	&	128,256	&	0.24    & 0.387 & 20.63 &  53.25    \\
$10^4$	&	256,512	&	0.084   & 0.15  & 180.82&  1205.25  \\
$10^5$	&	512,1024&	0.036   & 0.115 & 2757.73& 24061.75 \\
\\ \hline \hline \multicolumn{4}{c}{\vspace{-0.2cm}}\\
\multicolumn{4}{c}{\vspace{0.1cm}3D Runs} \\
\hline
$10^1$	&	32,	64$\times$64	& 2.29	& 106.15/61.5\\
$10^2$	&	64,	128$\times$128	& 0.69	& 111.92/185.35\\
$10^3$	&	128,256$\times$256	& 0.21	& 1426.39/6985.18\\
$10^4$	&	256,512$\times$512	& 0.068	& 23063.77/331,717\\
\hline																	
\end{tabularx}
\end{center}
\end{table}

The small differences between the SE and AE solutions for the case studied in 
Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
show the extreme power of AE.  In addition to the fact that AE runs require much
less total simulation time (see e.g., Fig.~\ref{fig:time_trace}a\&c and the time
values in the green highlighted regions), the first application of AE in a given
simulation (Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
increases the average timestep by immediately progressing the simulation into
a more converged state. For the $S = 10^5$ case we examined in detail, the
average time step grew by a factor of 2-3 due to the decreased convective
velocities from the transient state to the evolved state. 
At $S = 10^7$, the AE solve immediately improved the timestep size 
by nearly a factor of 4.
Thus, AE achieves converged solutions in few simulation time units,
while also taking less real world time per simulation time unit, when compared
to the slowly converging SE state at the same simulation time.

@@

\section{Discussion \& Conclusions}
\label{sec:extensions}
In this work we have studied a method of Accelerated Evolution (AE) which can
be employed to achieve rapid thermal equilibration of convective simulations.  We compared
this technique to the Standard Evolution (SE) of convection through a full thermal diffusion timescale,
and we
showed that AE rapidly obtains solutions whose dynamics are statistically similar to SE solutions.
The AE method is valid at low values of $S$, where SE solutions
converge quickly due to the short thermal timescale, and AE remains applicable
at high values of $S$, where SE solutions are intractable.
As discussed, AE is equally applicable in 2D and 3D; here we have restricted most of our study to 2D
to extend our parameter space coverage.
At the largest values of $S$ in which AE and SE are compared in this work, we find
time savings of nearly an order of magnitude. 
For example, in 2D and at $S = 10^5$, the
AE run took 10.78 wall hours on 256 cores ($2.8\cdot 10^3$ cpu-hours) while the 
SE run took 94 wall hours ($2.4\cdot 10^4$ cpu-hours). In 3D and at $S = 10^4$,
the AE run took 2.81 wall hours on 8192 cores ($2.3 \cdot 10^4$ cpu-hours),
while the SE run took 37.9 wall hours, or ($3.1 \cdot 10^5$ cpu-hours). As $S$ increases,
and the thermal time, $t_{\kappa}$, simultaneously increases, we anticipate the 
computational and wall hour time
savings to further increase.  The additional computational expense of 3D runs compared
to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.

Here we studied \RB convection with mixed thermal boundary
conditions as a test case for the AE method. There are many axes of complexity
which are beyond the scope of this work, but into which future work should explore
the correctness of AE. For example, the efficacy of AE at higher aspect ratios
where multiple stable solution branches exist at a given value of Ra should be
examined in order to determine if AE and SE obtain the same solution.

Some assumptions which inform the AE solution, for example that the convection
intially occupies the same space as the evolved convection, are large. It is
unclear if such an assumption would hold in more complex studies, such as those
of penetrative convection. However, techniques similar to AE have long been used
in such studies \cite{hurlburt&all1986}, so the careful testing of such a 
technique in domains with paired stable-unstable layers is key.

While over short timescales the AE method does not perfectly achieve the same
thermodynamic profile as the SE method (see e.g., the offset between the PDFs
in Fig.~\ref{fig:temp_comparison}b), the AE solution is \emph{close} to the SE
solution, and is achievable on dynamical timescales, which are computationally
tractable at high Ra, while thermal timescales (SE) are intractable. Thus,
while the AE solution is still evolving towards the SE solution over long thermal
timescales, the change in the structure over time is small 
(O(0.5\%), Fig.~\ref{fig:temp_comparison}c), and the dynamics of the AE solution 
and SE solution, which are often the most interesting part of a 
convective simulation to measure, are not massively different (e.g., 
Fig.~\ref{fig:parameter_space_comparison}d-f).

We anticipate that
this technique will be powerful in its extensions to more complicated studies.
To achieve AE in more complicated systems, one need only derive 
the steady-state, horizontally-averaged equations governing
the convective dynamics
(e.g., the analogs to Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple those equations with knowledge of the boundary conditions
and current dynamics as described in
section \ref{sec:ae} and appendix \ref{appendix:recipe}.
While in-depth studies of AE extensions are beyond the 
scope of this paper, we will briefly discuss
avenues in which AE should be explored and tested in order
to push interesting studies of various convective phenomena into
the astrophysically-interesting, high-Ra regime.

\begin{acknowledgments}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133.
\end{acknowledgments}

@@

>>>>

The Nusselt number (Nu) quantifies the efficiency of convective heat transport
and is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
The time evolution of Nu in AE and SE is compared to the mean temperature evolution
in Fig.~\ref{fig:nu_v_time}. The mean value of Nu evolves towards its final value
rapidly compared to the mean temperature. Thus, if Nu is the primary metric of 
the evolved flows being measured, it is unnecessary to run for a full thermal
time, and previous authors have taken advantage of this (CITE).
When $S < 10^{3.67}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a time-stationary value of Nu, and is thus
in a state of constant convective heat transport.
At larger $S$ in 2D, the value of Nu varies significantly over time,
as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
AE runs in Fig.~\ref{fig:oscillating_plumes}. We find that these systems exhibit
large Nu during
states in which temperature fluctuations travel in their natural buoyant
direction (Fig.~\ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
with oppositely signed fluid, Nu is suppressed (Fig.~\ref{fig:oscillating_plumes}, Ib and IIb, 
where warm fluid is pulled down by the downflow
lane, and cool fluid is drawn up by the upflow lane). High-transport and 
low-transport states exhibit smaller Nu fluctuations away from the 
mean once the system reaches thermal equilibrium (Fig. \ref{fig:nu_v_time}).
The plumes in these
systems naturally oscillate horizontally over time, switching between transport being dominated
by a counterclockwise cell, as pictured in Fig.~\ref{fig:oscillating_plumes}, and
a clockwise cell. Our choice of no-slip
boundary conditions prevents the fluid from entering a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable. However, thanks to our choice of periodic
boundary conditions and despite the no-slip conditions, the full system of the
upflow and downflow plumes is free to slowly migrate to the left or right over time,
and we observe this phenomenon in our solutions.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. 
This time-dependent behavior of Nu is not seen strongly in our 3D solutions,
however most 3D simulations we conducted were at low $S$ compared to the runs in
which this behavior was observed in 2D.

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
\caption{Here we compare the time evolution of the mean temperature and the
Nusselt number for the 2D SE and AE run shown in Fig.~\ref{fig:time_trace}.
\label{fig:nu_v_time} }
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
\caption{The time variation of the Nusselt number is shown for two AE cases at
$S = 10^5$ (top) and $S = 10^7$ (bottom). On the left, the instantaneous value of Nu
is shown as a function of time. On the right, temperature snapshots are shown for
Nu maxima (Ia \& IIa) and minima (Ib \& IIb). The suppressed value of Nu at the
minma arises from entrainment of fluid elements whose temperature perturbations
are wrongly signed (e.g., hot material going downwards and cold material going
upwards in Ib \& IIb). The colorbar scaling of panels Ia\&b are the same, as
are the scalings of panels IIa\&b. 
The minimum temperature is chosen by the fixed-temperature
boundary condition at the top, $T_{\text{top}} = -0.5$. The decreased range of
the colorbar scaling for
for IIa\&b was chosen to better display the convective dynamics.
\label{fig:oscillating_plumes} }
\end{figure}

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement and denote 2D (purple circles) and 3D (red stars). 
The run at $S = 10^5$ marked as a
black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
Vertical lines represent the standard deviation of the measurement,
and quantify natural variation over the averaging window. 
(a) Nu scales as Ra$^{1/5}$; at high $S$ in 2D the value of Nu fluctuates over time
(see Fig.~\ref{fig:oscillating_plumes}).  
(b) Re, which measures turbulence in the solution, scales as
Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at the fixed-temperature
top boundary is shown; this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
Relative error for measurements of (d) Nu, (e) Re, and (f) $\angles{T} - T_{\text{top}}$ between 
AE solutions and SE solutions are shown.
The greyed area of the plots indicates the region in which only AE runs were
carried out due to computational expense. \label{fig:parameter_space_comparison} }
\end{figure}

@@

\begin{figure}[b!]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
(d-f) The KS profiles, as defined in Eqn.~(\ref{eqn:ks_profile}),
are shown for the related distributions; solid lines indicate positive values
while dashed lines are negative values. Unlike the temperature distributions in
Fig.~\ref{fig:temp_comparison}, these distributions
show very good agreement and small values of the KS statistic.
\label{fig:pdf_comparison} }
\end{figure}

%%%%%%%%%%%%
%%%%%%%%%%%
% SPEEDINESS OF AE vs SE
%%%%%%%%%%%
%%%%%%%%%%%%
\newpage$\,$\newpage
\section{Computational Benefits of AE}
\label{sec:speedups}

\begin{table}
\caption{
}
\label{table:speed}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X}
\hline																	
$S$	&	nz, nx, ny	&	$t_{\text{sim,AE}}/t_{\text{sim,SE}}$	&	
$t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$ & $t_{\text{CPU,AE}}$ & $t_{\text{CPU, SE}}$		\\
\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
\multicolumn{6}{c}{\vspace{0.1cm}2D Runs} \\
\hline
$10^2$	&	64,	128	&	0.905   & 2.03  & 4.369 &  2.152    \\
$10^3$	&	128,256	&	0.24    & 0.387 & 20.63 &  53.25    \\
$10^4$	&	256,512	&	0.084   & 0.15  & 180.82&  1205.25  \\
$10^5$	&	512,1024&	0.036   & 0.115 & 2757.73& 24061.75 \\
\hline \hline \multicolumn{6}{c}{\vspace{-0.2cm}}\\
\multicolumn{6}{c}{\vspace{0.1cm}3D Runs} \\
\hline
$10^1$	&	32,	64$\times$64	& 2.29	& 1.73  &   106.15      &   61.5\\
$10^2$	&	64,	128$\times$128	& 0.69	& 0.6   &   111.92      &   185.35\\
$10^3$	&	128,256$\times$256	& 0.21	& 0.2   &   1426.39     &   6985.18\\
$10^4$	&	256,512$\times$512	& 0.068	& 0.07  &   23063.77    &   331,717\\
\hline																	
\end{tabularx}
\end{center}
\end{table}

The primary reason to use AE, rather than evolving all solutions through SE,
is because of the computational timesaving of such an approach. In table 
\ref{table:speed}, we compare simulation time and cpu-hour cost for select
2D and 3D runs in which AE and SE solutions were compared. Times reported
for AE and SE runs do not include the time over which measurements were taken
in the equilibrated state, but rather represent the time required to reach a
fully equilibrated state under the AE or SE formalism. All simulations
were performed on Broadwell nodes on NASA's Pleiades supercomputer 
(Intel Xeon E5-2680v4 processors). The key metric which highlights the usefulness
of AE is the number of cpu-hours used for the AE run in units of cpu-hours used
for the SE run ($t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$). We see that at low
resolution and low supercriticality, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}} > 1$,
and AE is not useful. However, as $S$ grows, $t_{\text{CPU,AE}}/t_{\text{CPU,SE}}$
shrinks. At the highest supercriticalities for which AE and SE were compared
in this work, AE runs cost roughly an order of magnitude less computing time 
than SE runs.
 The additional computational expense of 3D runs compared
to 2D runs implies that 3D studies can greatly benefit from the proper implementation of AE.

While storing information about the mean state for the AE solve marginally
decreases the rate at which our solver timesteps, the first application of AE in a given
simulation (Fig.~\ref{fig:time_trace}c, at the arrow labeled ``1'') drastically
increases the average timestep by immediately progressing the simulation into
a more converged state. For the $S = 10^5$ case we examined in detail, the
average time step grew by a factor of 2-3 due to the decreased convective
velocities from the transient state to the evolved state. 
At $S = 10^7$, the AE solve immediately improved the timestep size 
by nearly a factor of 4.

@@

\section{Discussion \& Conclusions}
\label{sec:extensions}
In this work we have studied a method of Accelerated Evolution (AE) which can
be employed to achieve rapid thermal equilibration of convective simulations.  We compared
this technique to the Standard Evolution (SE) of convection through a full thermal diffusion timescale,
and we
showed that AE rapidly obtains solutions whose dynamics are statistically similar to SE solutions.
The AE method is valid at low values of $S$, where SE solutions
converge quickly due to the short thermal timescale, and AE remains applicable
at high values of $S$, where SE solutions are intractable.
As discussed, AE is equally applicable in 2D and 3D; here we have restricted most of our study to 2D
to extend our parameter space coverage.
At the largest values of $S$ in which AE and SE are compared in this work, we find
time savings of nearly an order of magnitude.

Here we studied the simplest possible case for the application of AE:
\RB convection at low aspect ratio with mixed thermal boundary. 
We anticipate that
this technique will be powerful in its extensions to more complicated studies.
To achieve AE in more complicated systems, one need only derive 
the steady-state, horizontally-averaged equations governing
the convective dynamics
(e.g., the analogs to Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple those equations with knowledge of the boundary conditions
and current dynamics as described in
section \ref{sec:ae} and appendix \ref{appendix:recipe}.
In general, AE should be useful in studies where there are two disparate
timescales which must both be resolved and which cannot be overcome through
clever timestepping techniques.  Some avenues in which extensions of AE could
be beneficial for expanding the available parameter space of exploration
include studies of internally heated convection \cite{goluskin2016},
convection with height-dependent conductivities \cite{kapyla&all2017},
penetrative convection \cite{hurlburt&all1986,brandenburg&all2005,couston&all2017},
or fully compressible, stratified convection \cite{anders&brown2017}.

We conclude by noting that AE should be extended to these more complicated
studies with care. 
While AE was extremely effective in this simple case studied here
(where the aspect ratio was low, 
the bounds of the convective domain were pre-defined,
and the solutions were simple rolls),
this may not be the case for more complicated systems. For example, at
higher aspect ratios, multiple stable solution branches of various numbers of
convective rolls may exist, and there is no guarantee that AE and SE will
arrive at the same solution. 
Some assumptions which inform the AE solution, such as the assumption
that the convection
intially occupies the same space as the evolved convection, may not hold in
studies of penetrative convection, despite the fact that similar methods have
long been used in those studies \cite{hurlburt&all1986}.
Our work here should serve as a basis for determining if AE techniques are
valid and effective in more complex studies of convection.

\begin{acknowledgments}
We thank the two anonymous referees whose careful comments greatly 
improved the clarity and scientific content of this paper.
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with the support of the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocation GID s1647.
\end{acknowledgments}

@@

In general, the user of the AE method should choose some threshold
fractional change of the mean temperature profile, $f$, such that once
an AE solution differs from the DNS mean profile by less than $f$, the simulation
is considered converged and the iterative AE adjustments may be stopped. In
other words, once
\begin{equation}
\frac{|\angles{T}_{\text{DNS}} - \angles{T}_{\text{AE}}|}{|\angles{T}_{\text{DNS}}|} < f,
\end{equation}
the solution is converged. In this work, we chose our number of AE iterations
such that $f \approx 10^{-2}$, except at $S = 10^7$, where we stopped after one AE
iteration due to higher computational expense. In general, the user of AE could
set $f$ smaller, and in doing so reduce the separation between the AE and SE
solutions, which can be seen in e.g., Fig.~\ref{fig:temp_comparison}.
